Inducing Semantic Frames on a Very Large Corpus of Syntactic-Ngrams

### 2015-01-05 Paper/paperN.tex

\begin{abstract}
We explore two models for the unsupervised induction of semantic frames on a 
very large corpus of verb-subject-object triples. Our work is bade on previous 
research that has had success on smaller, more focused data sets. By encouraging 
verb sparsity with a Dirichlet prior, one can improve on the results of our 
baseline model. We give some analysis of the frames that the improved model 
discovers, and suggest areas for further development.
\end{abstract}

@@

%\section{Related Work}
We based our work on two papers: \textit{`Inducing a semantically annotated lexicon via em-based clustering.'} by \citeauthor{rooth1999} and \textit{`Learning frames from text with an unsupervised latent variable model.'} by \citeauthor{oconnor2013}. In the first article clustering is realized by applying expectation maximization on a simple cooccurance model. This model produces frames in the form of two distributions, one for the predicate, a distribution over verbs, and one for the arguments, a nouns. Following O'Connor, we modify this model slightly to accommodate verb-subject-object triples. A triple is assigned to the frame for which is probability of occurring is highest. We will use this model as our baseline (as in the O'Connor paper). The second paper covers two additional models, of which we implemented one. This model differs from the baseline model by introducing the assumption that a document generates sentences frame a restricted set of frames. This assumption is justified (as in latent Dirichlet allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics. In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.

>>>>

\begin{abstract}
We explore two models for the unsupervised induction of semantic frames on a 
very large corpus of verb-subject-object triples. Our work is bade on previous 
research that has had success on smaller, more focused data sets. By encouraging 
verb sparsity with a Dirichlet prior, one can improve on the results of our 
baseline model. We give some analysis of the frames that the improved model 
discovers, and suggest areas for further development.

  Information in text can be represented by frames. A frame consists of a predicate with arguments. In this report we discuss two probabilistic latent variable models which are trained by resp. expectation maximization and Gibbs sampling, to induce frames from syntactic tri-grams of the form: verb, subject, object. The latent variable is the frame a verb belongs to. In practice, the models cluster verbs based on the occurrences of arguments they are encountered with. The frames (or clusters of verbs) are measured by correctness (relative to each other) and correctness (relative to FrameNet clusters). The more suffisticated second model performs well and finds clusters of verbs which have a distinct general meaning, the frames induced with the simple model 0 are not as well defined as thos of model 1. 
\end{abstract}

@@

%\section{Related Work}
We based our work on two papers: \textit{`Inducing a semantically annotated lexicon via em-based clustering.'} by \citeauthor{rooth1999} and \textit{`Learning frames from text with an unsupervised latent variable model.'} by \citeauthor{oconnor2013}. In the first article clustering is realized by applying expectation maximalization on a simple cooccurance model. This model produces frames in the form of two distributions, one for the predicate, a distribution over verbs, and one for the arguments, a nouns. Following O'Connor, we modify this model slightly to accomodate verb-subject-object triples. A triple is assigned to the frame for which is probability of occuring is highest. We will use this model as our baseline (as in the O'Connor paper). The second paper covers two additional models, of which we implemented one. This model differs from the baseline model by introducing the assumption that a document generates sentences frome a restricted set of frames. This assumption is justified (as in latent Dirichelt allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics and thus use a proper subset of the frames. In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.
